---
title: "HW3"
author: "Nick Kim"
format: html
---

Link to my [github](https://github.com/nick-kimm/HW3) repository 

## Problem 1

#Part a: 
Reading Data Files 
```{r}
library(haven)

v_file <- "/Users/nicholaskim/Documents/STAT 506/HW3/VIX_D.XPT"
vision <- read_xpt(v_file)

d_file <- "/Users/nicholaskim/Documents/STAT 506/HW3/DEMO_D.XPT"
demo <- read_xpt(d_file)
```

Merging into one dataframe:
```{r}
mdata<-merge(vision,demo)
#Checking if its a data frame
print(is.data.frame(mdata))
#Showing it reduced the size of the dataframe to only that matched
print(c(nrow(demo),nrow(mdata)))
```

#Part b:
Proportion of respondents in each 10 year bands. From the DEMO doc we know all possible range of values is 0-84 yrs
```{r}
#remove all rows where there is no age recorded:
mdata<-mdata[is.na(mdata$RIDAGEMN)!=TRUE,]

#remove all rows where there is NA or 9 (don't know) for if the respondent wears glasses/contacts
mdata<-mdata[is.na(mdata$VIQ220)!=TRUE & mdata$VIQ220!=9,]

#this will store the total count of individuals in each 10 year band into one vector
tages <- vector(length=9)
#this will store the total count of individuals who wear either glasses or contacts
gccount <- vector(length=9)
#this will store the percentage that wear glasses or contacts in there respective age group
pgc <- vector(length=9)

for (i in 1:9){
  tages[i] <- nrow(mdata[((mdata$RIDAGEMN/12)<(i*10)&(mdata$RIDAGEMN/12)>((i-1)*10)),])
  gccount[i] <- nrow(mdata[mdata$VIQ220==1&((mdata$RIDAGEMN/12)<(i*10)&(mdata$RIDAGEMN/12)>((i-1)*10)),])
  pgc[i] <- (gccount[i]/tages[i])*100
}
```



```{r}
library(knitr)
library(kableExtra)

prop<-t(data.frame("Num Wears Glasses/Contacts"=format(round(gccount, 0), nsmall = 0),"Total in Age Group"=format(round(tages, 0), nsmall = 0),"Per Who Wear Glasses/Contacts"=format(round(pgc, 2), nsmall = 2)))

colnames(prop)<-c("0-9","10-19","20-29","30-39","40-49","50-59","60-69","70-79","80-89")

prop%>%
  kbl(caption = "Percentage of Respondents Who Wear Glasses/Contacts in 10 yr Bands")%>%
  kable_paper()%>%
  add_header_above(c("Ages"=10))%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```


#Part c:
Fitting logistic regression models:

Model 1:
Just Age as predictor

First we'll be changing the value of VIQ220 (whether they wear glasses/contacts) to a bionomial variable since GLM requires it to be in between the values of 0 to 1.
```{r}
mdata$VIQ220 <- ifelse(mdata$VIQ220==2,0,1)
```

Running the Logistic Regression Model
```{r}
mod1<-glm(VIQ220~RIDAGEMN,data=mdata,family=binomial)
summary(mod1)
```

Model 2:
Age, Race, and Gender as predictor variables
```{r}
mod2<-glm(VIQ220~RIDAGEMN+RIDRETH1+RIAGENDR,data=mdata,family=binomial)
summary(mod2)
```

Model 3:
Age, Race, Gender, and Poverty Income Ratio as predictor variables
```{r}
mod3<-glm(VIQ220~RIDAGEMN+RIDRETH1+RIAGENDR+INDFMPIR,data=mdata,family=binomial)
summary(mod3)
```
```{r message=FALSE, results='asis'} 
library(stargazer)

stargazer(mod1, mod2, mod3, type = "html")
```
Creating one table output
```{r}
coeffs <- 
mod1$coefficients
summary(mod1)$df
summary(mod1)$null.deviance
```

Defining a helper function
```{r}
#' db function
#'This function will shorten the function name we will call when using dbConnect for ease of use for the user
#' @param connection 
#' @param query 
#'
#' @return output from dbConnect function
gg <- function(connection,query){
  dbGetQuery(connection,query)
}
```